---
title: "Motivation"
header-includes:
   - \usepackage{bbm}
   - \usepackage{amsmath,latexsym}
   - \newcommand{\bm}[1]{\mbox{\boldmath $#1$}}
keep_tex: yes
output: pdf_document
number_sections: true
documentclass: article
toc: yes
toc_depth: 3
---

```{r include = FALSE}
library(viridis)
library(INLA)
library(inlabru)
```
\section{Intro}
Somebody who opesm this book might wonder -- it this book for me? 
  
Many data sets with data structures that seem to be different initially.

Spatial component that has not been traditionally pointed out/discussed.

\section{Examples}

\subsection{Spatially continuous data}

```{r}
data(gorillas) # get the data
 gcov = gorillas$gcov

 # Plot the elevation covariate
 plot(gcov$elevation) 
```

\subsection{Spatial point patterns}
\subsection{Data collected on transects}
\subsection{Distance sampling data}


People with spatial data 

$\sum \mathbb{R} \bm{x} \times 4$

```{r}
data(gorillas) # get the data
 # extract all the objects, for convenience:
 nests = gorillas$nests
 mesh = gorillas$mesh
 boundary = gorillas$boundary
 gcov = gorillas$gcov
 gnestsamples = gorillas$plotsample
 
 # plot all the nests, mesh and boundary
 ggplot() + gg(mesh,lwd=0.1) + gg(boundary) + gg(nests, pch="+",cex=2)
 
 # Plot the elevation covariate
 plot(gcov$elevation) 
 
 # Plot the plot sample
 ggplot() + gg(gnestsamples$nests) + gg(gnestsamples$plots)
```


